Windowed Developer Topic Analysis

### 2009-03-31 lda-paper.tex
modified the lda paper some more?

>>>>

Once stop words were removed the some of hte purposes became more
clear. The mega trend disappeared, the largest trend became bug fixes
submitted by Dal Zotto which is a short trend.

% Large Trends is not the point!!!
% That's what normal LDA gives us

But large trends are not the point, by investigating windowed trends
we want more local information about trends being worked on.
